Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-20 Report/mse_formulation.tex
updated with Nam changes (half cooked)

In the second method, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{equation} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{equation}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \nonumber \\	
	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}}
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
			$j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}, which is in fact a \ac{DC} constraint. We resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
\label{mse-lin}
\end{IEEEeqnarray}

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for a fixed receive beamformer. The optimization subproblem to find the transmit precoders for a fixed receive beamformer \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for a fixed receiver are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}. The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.

>>>>

In the second method, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{equation} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{equation}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. Note that the receive beamformers based on the \ac{MMSE} criterion are independent of the choice of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represent the weighted formulation. By using the relaxed \ac{MSE} expression in \eqref{mse-error}, we can reformulate \eqref{eqn-3} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \nonumber \\	
	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}}

The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}. Again we resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using the first order Taylor approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
\label{mse-lin}
\end{IEEEeqnarray}

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for fixed receive beamformers. The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}. The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.

### 2015-07-20 Report/problem_formulation_intro.tex
updated with Nam changes (half cooked)

For practical reasons, we impose a constraint on the maximum number of transmitted bits for the user \me{k}, since it is limited by the total number of backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of norm \me{\ell_q} in the objective of \eqref{eqn-3}. Suppose that \me{t_k>Q_k} for certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that the optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows.
\begin{itemize}
\item \me{\ell_{1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel conditions before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
\item \me{\ell_{2}} prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item \(\ell_{\infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

>>>>

For practical reasons, we impose a constraint on the maximum number of transmitted bits for the user \me{k}, since it is limited by the total number of backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
\end{equation}
The above positivity constraint needs to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of \me{\ell_q} norm in the objective of \eqref{eqn-3}. Suppose that \me{t_k>Q_k} for a certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a strictly smaller objective which contradicts with the fact that the optimal solution has been obtained. The choice of \me{\ell_q} norm used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows.
\begin{itemize}
\item \me{\ell_{1}} norm results in greedy allocation \textit{i.e}, emptying the queue of users with good channel states before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
\item \me{\ell_{2}} norm prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item \(\ell_{\infty} \) norm minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating resources proportional to the number of backlogged packets.
\end{itemize}

### 2015-07-20 Report/simulation_distributed.tex
before sending to nam and antti
updated with Nam changes (half cooked)

The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update. Fig. \ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets, \review{with} the queued packets for each user is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
	\label{fig-d-3.1}
\end{figure}

Fig. \ref{fig-d} compares the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation using the number of backlogged packets. In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables. The number of backlogged packets only at the \ac{SCA} points are marked in the figure. The performance of the distributed approaches are similar to the centralized schemes if the primal and dual updates are performed until convergence. %In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. %It can be seen from Fig. \ref{fig-d} that the distributed algorithms approach the centralized scheme by exchanging minimal information between the coordinating \acp{BS}.

Fig. \ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB. The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}. A heuristic method is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0} to addresses the over-allocation. The heuristic approach oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}. The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
\begin{figure*}
	\centering
	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
		\includegraphics[width=0.48\textwidth]{average_queue_over_time-3}
		\label{fig-review}
	}
	\hfill
	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-3}
		\label{fig-review-time}
	}
	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace}}
	\label{fig-time-analysis}
\end{figure*}

>>>>

The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update. Fig. \ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB and each \ac{BS} serves \me{|\mc{U}_b| = 4} users. As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size \eqn{\rho^{(i)}}. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
	\label{fig-d-3.1}
\end{figure}

Fig. \ref{fig-d} compares the performance of the \ac{JSFRA} schemes discussed in Sections \ref{sec-3.2.1} and \ref{sec-3.3} using primal and \ac{ADMM} approaches. For each \ac{SCA} update, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables. The number of backlogged packets only at the \ac{SCA} points are marked in the figure. The performance of the distributed approaches is similar to that of the centralized schemes if the distributed algorithms are allowed converge. However, in our simulations, we observe that \eqn{J_{\max} = 20} is sufficient for the \ac{ADMM} to converge. %In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. %It can be seen from Fig. \ref{fig-d} that the distributed algorithms approach the centralized scheme by exchanging minimal information between the coordinating \acp{BS}.

Fig. \ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB. The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy nature of the objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}. A heuristic method is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0} to addresses the over-allocation. The heuristic approach oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}. The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
\begin{figure*}
	\centering
	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
		\includegraphics[width=0.48\textwidth]{average_queue_over_time-3}
		\label{fig-review}
	}
	\hfill
	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-4}
		\label{fig-review-time}
	}
	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace}}
	\label{fig-time-analysis}
\end{figure*}
